%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Research Engineer} % Job title
    {MIALAB --- Medical Imaging Analysis Laboratory, UPV} % Organization
    {Valencia, Spain} % Location
    {May 2024 -- Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Architected a semantic segmentation pipeline for brain MRI analysis (700k+ volumes) using U-Net variants with Attention Mechanisms, achieving state-of-the-art parcellation accuracy.}
        \item {Optimized legacy research code for training and inference, significantly reducing computation time and preparing models for production deployment on the VolBrain neuroimaging platform.}
        \item {Validated segmentation models against expert neuroanatomical annotations, ensuring clinical-grade reliability across heterogeneous MRI acquisitions.}
        \item {Modernized lab engineering practices: implemented private Gitlab, modular code architecture, and reproducible experiment tracking to a previously ad-hoc research workflow.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Co-Founder \& CTO} % Job title
    {Mycrospace --- Biotech Startup} % Organization
    {Valencia, Spain} % Location
    {Jan. 2024 -- Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and deployed a proprietary Computer Vision system for automated microbial colony counting, achieving 95\% median MAPE against expert microbiologist ground truth.}
        \item {Engineered custom model architectures---YOLO-based detectors and Density Map Regressors---to handle high-density overlapping objects ($>$300 colonies per plate).}
        \item {Curated a specialized dataset of 3,500 annotated images across 12 microbial species, validating ground truth labels in collaboration with domain microbiologists.}
        \item {Built the full ML infrastructure: data ingestion pipelines, PyTorch training framework, and scalable inference API deployed on Google Cloud Platform with Docker.}
        \item {Delivered full-stack product development (Next.js, Cloud) as a secondary enabler, enabling rapid iteration from research prototype to production SaaS.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Product Developer --- Internship} % Job title
    {Vesta-Z} % Organization
    {Valencia, Spain} % Location
    {2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed full-stack cloud-based product features, gaining production experience in scalable web architectures and deployment workflows.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {AI Research Intern --- Industrial Bachelor's Project} % Job title
    {Neurocatching} % Organization
    {Valencia, Spain} % Location
    {2022 -- 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed ML models for ocular movement analysis applied to neuromarketing, engineering end-to-end pipelines from raw gaze data to predictive inference.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {ML Engineering Intern} % Job title
    {Sciling} % Organization
    {Valencia, Spain} % Location
    {2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Gained early exposure to large language models (GPT-2/3), Diffusion Models, and IBM Watson, contributing to applied NLP and generative AI projects.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
